Velocity Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$: a benchmark study of vibronic coupling interactions

### 2022-04-14 Aug2021-CH2-.tex
fix table
cse

\begin{figure}
	\includegraphics[width=0.8\textwidth]{figures/Fig1}
	\caption{(a) A 3D-representation of the velocity-map image of $\sim$ 4 million photoelectrons detached from C$2$H$^-$ at 355~nm. The outer rings, distributed around the vertical laser polarisation axis, represents photodetachment to the ground $\tilde{X}\,^2\Sigma^+$ state. The inner rings reprsent detachment to the first excited state $\tilde{A}\,^2\Pi$. (b) Photoelectron spectra of C$_2$H$^-$ at a range of detachment wavelengths, illustrating the change in electron intensity profile and energy resolution.}
	\label{fig:1}
\end{figure}

@@

\begin{table}
	\caption{Parameters for the quasidiabatic Hamiltonian Eq.~(\ref{eq:calc1}) determined using CFOUR and the quasidiabatic ansatz.}
	\label{tab:1}
	\begin{tabular}{c |c c c c| c c c c }
		 & C$_2$H & &  & & C$_2$D & & & \\
		  & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ \\
		 \hline\hline
		 $\Delta$E & 0 & 22431.21 &  26543.67 & 26543.67 & 0&	22431.21 & 26543.67	& 26543.67\\
		 f1 & 0	& -211.28 & 286.9 &	286.9 & 0& -596.04& 641.6 & 641.6\\
		 f2 & 0 & -1515.21 & 1257.07 & 1257.07 & 0 & -1401.53 & 1115.17 & 1115.17\\
		 f3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
		 f4 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
         f11 & 3424.32 & 3487.03 & 3482.16 & 3482.16 & 2611.42 & 2636.57 & 2681.25 & 2681.25\\
         f12 & 0.00 & -28.32 & 31.46 & 31.46 & 0.00 & -48.38 & 55.40 & 55.40\\
         f22 & 1894.71 & 1830.83 & 2099.57 & 2042.21 & 1792.49 & 1747.62 & 1914.39 & 1914.39\\
         f33 & 607.09 & 87.57 & 1883.48 & 658.96 & 481.89 & 120.09 & 1503.88 & 473.55\\
         f44 & 607.09 & 87.57 & 658.96 & 1883.48 & 481.89 & 120.09 & 473.55 & 1503.88\\
         $\lambda$ &  & & -1185.26 &  &  & & -1014.58 &  \\
         \end{tabular}
\end{table}

>>>>

\begin{figure}
	\includegraphics[width=0.8\textwidth]{figures/Fig1}
	\caption{(a) Velocity map image of C$_2$H$^-$ photodetachment at 355~nm. (b) Velocity map image of C$_2$D$^-$ at 355~nm. (c) Comparison of 355~nm photoelectron spectra from C$_2$H$^-$ and C$_2$D$^-$. Structure below $\sim 27,000~$cm$^{-1}$ is assigned to the ground state $\tilde{X} ^2\Sigma^+$, and structure above  $\sim 27,000~$cm$^{-1}$ is assigned to the excited $\tilde{A} ^2\Pi$ state.}
	\label{fig:1}
\end{figure}

@@

\begin{table}
	\caption{Parameters for the quasidiabatic Hamiltonian Eq.~(\ref{eq:calc1}) determined using CFOUR and the quasidiabatic ansatz.}
	\label{tab:1}
	\begin{tabular}{c |c c c c| c c c c }
		 & \multicolumn{4}{c}{C$_2$H}     & \multicolumn{4}{c}{C$_2$D}  \\ \hline
		  & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ & Anion & $\tilde{X}^2\Sigma^+$ & $\tilde{A}^2\Pi (a')$ & $\tilde{A}^2\Pi (a'')$ \\
		 \hline\hline
		 $\Delta$E & 0 & 22431.21 &  26543.67 & 26543.67 & 0&	22431.21 & 26543.67	& 26543.67\\
		 f1 & 0	& -211.28 & 286.9 &	286.9 & 0& -596.04& 641.6 & 641.6\\
		 f2 & 0 & -1515.21 & 1257.07 & 1257.07 & 0 & -1401.53 & 1115.17 & 1115.17\\
		 f3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
		 f4 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
         f11 & 3424.32 & 3487.03 & 3482.16 & 3482.16 & 2611.42 & 2636.57 & 2681.25 & 2681.25\\
         f12 & 0.00 & -28.32 & 31.46 & 31.46 & 0.00 & -48.38 & 55.40 & 55.40\\
         f22 & 1894.71 & 1830.83 & 2099.57 & 2042.21 & 1792.49 & 1747.62 & 1914.39 & 1914.39\\
         f33 & 607.09 & 87.57 & 1883.48 & 658.96 & 481.89 & 120.09 & 1503.88 & 473.55\\
         f44 & 607.09 & 87.57 & 658.96 & 1883.48 & 481.89 & 120.09 & 473.55 & 1503.88\\
         $\lambda$ &  & & -1185.26 &  &  & & -1014.58 &  \\
         \end{tabular}
\end{table}
